\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-05-07 doc/sw-system.tex
Fixed #167, fixed#168, fixed #169

The \cfhtls $g$, $r$ and $i$-band images have the greatest average
depth and highest average image
quality of the survey,
and we chose to focus on this subset. (The remaining $u$ and $z$-band images
were also made available for perusal in \Talk). We made colour composite PNG
format images following the prescription of \citet{LuptonEtal2004} \citep[with
extensions by][and some particular choices of our own]{WherryEtal2004}, using
the \humvi software.\footnote{The \humvi colour image composition code used in
this work is open source and available from
\texttt{http://github.com/drphilmarshall/HumVI}} Specifically, we first rescaled
the pixel values of each image, in the notation of \citeauthor{LuptonEtal2004},
into flux units (``picomaggies,''), via the image AB zeropoint $m_0$ and the
pixel value calibration factor $f$  given by $\log_{10}{f} = 0.4(30.0 - m_0)$.
We then multiplied these calibrated images by further aesthetic ``scales''
$s_{i,r,g}$ before computing the total intensity image $I$ and applying an
arcsinh stretch. (The scales are re-normalized to sum to one on input.) Thus,
the red ($R$), green ($G$) and blue ($B$) channel images correspond to the
\cfhtls $i$, $r$ and $g$-band images in the following way:
\bea
I & = & (i \cdot s_i + r \cdot s_r + g \cdot s_g), \notag \\
R & = & i \cdot s_i \cdot \frac{{\rm asinh}\left(\alpha \cdot Q \cdot I\right)}{Q \cdot I}, \notag \\
G & = & r \cdot s_r \cdot \frac{{\rm asinh}\left(\alpha \cdot Q \cdot I\right)}{Q \cdot I}, \notag \\
B & = & g \cdot s_g \cdot \frac{{\rm asinh}\left(\alpha \cdot Q \cdot I\right)}{Q \cdot I}. \notag \\
\eea
We chose to allow the composite image formed from these channel images to
saturate to white: any pixels in any of the channel images lying outside the
range 0 to 1 was assigned the value 0 or 1 appropriately. This was not the
recommendation of \citet{LuptonEtal2004}, but we found it to still give very
informative but also familiar-looking astronomical images.

@@

These parameters were then fixed during the production of all the tiles, in
order to allow straightforward comparison between one image and another, and
for intuition to be built up about the appearance of stars and galaxies across
the survey. Alternative algorithms, such as adjusting the stretch and scale
dynamically according to, for example, the root-mean-square pixel value in
each image, can lead to better presentation of bright objects, but in doing so
they tend to hide the faint features in those images: we needed to optimize
the detectability of these faint features.   Examples of \cfhtls training set
images prepared in this way can be seen in the galleries of the previous
section (Figures~\ref{fig:training-gallery:sims}
and~\ref{fig:training-gallery:duds}). We also defined two alternative sets of
visualization parameters, to display a ``bluer'' image and a ``brighter''
image in the classification interface Quick Dashboard
(\Sref{sec:design:interface}). The QD code performs the same image composition
as just described, but dynamically on FITS images in the browser. These FITS
images are also available for viewing in \Talk, via the main Zooniverse
Dashboard image display tool, which again offers the same stretch settings, as
a starting point for image exploration. Our parameter choices are given in
\Tref{tab:data:humvi}.

@@

Each classification made is logged in a database, storing subject IDs,
(anonymous) volunteer IDs, a timestamp and the classification results (the image
pixel-coordinate positions of every marker placed).  The ``category'' of subject --
whether it is a ``training'' subject (a simulated lens or a known non-lens) or a
``test'' subject (an unseen image drawn from the survey) -- is also recorded.
For training subjects, we also store the ``kind'' of the subject as
a lens (``sim''), or a non-lens (``dud''), and also the ``flavour'' of lens
object if one is present in the image (``lensed galaxy'', ``lensed quasar'' or
``cluster lens'').  This classification is used to provide instant feedback, but
is also the basic measurement used in a probabilistic classification of every
subject based on all image views to date. Not all
volunteers register with the Zooniverse (although all are prompted to do so);
in these cases we record their IP addresses as substitute IDs.

>>>>

The \cfhtls $g$, $r$ and $i$-band images have the greatest average
depth and highest average image
quality of the survey,
and we chose to focus on this subset. (The remaining $u$ and $z$-band images
were also made available for perusal in \Talk). We made colour composite PNG
format images following the prescription of \citet{LuptonEtal2004} \citep[with
extensions by][and some particular choices of our own]{WherryEtal2004}, using
the \humvi software.\footnote{The \humvi colour image composition code used in
this work is open source and available from
\texttt{http://github.com/drphilmarshall/HumVI}} Specifically, we first rescaled
the pixel values of each image, in the notation of \citeauthor{LuptonEtal2004},
into flux units (``picomaggies''), via the image AB zeropoint $m_0$ and the
pixel value calibration factor $f$  given by $\log_{10}{f} = 0.4(30.0 - m_0)$.
We then multiplied these calibrated images by further aesthetic ``scales''
$s_{i,r,g}$ before computing the total intensity image $I$ and applying an
arcsinh stretch. (The scales are re-normalized to sum to one on input.) Thus,
the red ($R$), green ($G$) and blue ($B$) channel images correspond to the
\cfhtls $i$, $r$ and $g$-band images in the following way:
\bea
I & = & (i \cdot s_i + r \cdot s_r + g \cdot s_g), \notag \\
R & = & i \cdot s_i \cdot \frac{{\rm asinh}\left(\alpha \cdot Q \cdot I\right)}{Q \cdot I}, \notag \\
G & = & r \cdot s_r \cdot \frac{{\rm asinh}\left(\alpha \cdot Q \cdot I\right)}{Q \cdot I}, \notag \\
B & = & g \cdot s_g \cdot \frac{{\rm asinh}\left(\alpha \cdot Q \cdot I\right)}{Q \cdot I}. \notag \\
\eea
We chose to allow the composite image formed from these channel images to
saturate to white: any pixels in any of the channel images lying outside the
range 0 to 1 was assigned the value 0 or 1 appropriately. This was not the
recommendation of \citet{LuptonEtal2004}, but we found it to still give very
informative but also familiar-looking astronomical images.

@@

These parameters were then fixed during the production of all the tiles, in
order to allow straightforward comparison between one image and another, and
for intuition to be built up about the appearance of stars and galaxies across
the survey. Alternative algorithms, such as adjusting the stretch and scale
dynamically according to, for example, the root-mean-square pixel value in
each image, can lead to better presentation of bright objects, but in doing so
they tend to hide the faint features in those images: we needed to optimize
the detectability of these faint features.   Examples of \cfhtls training set
images prepared in this way can be seen in Figures~\ref{fig:training-gallery:sims}
and~\ref{fig:training-gallery:duds}. We also defined two alternative sets of
visualization parameters, to display a ``bluer'' image and a ``brighter''
image in the classification interface Quick Dashboard
(\Sref{sec:design:interface}). The QD code performs the same image composition
as just described, but dynamically on FITS images in the browser. These FITS
images are also available for viewing in \Talk, via the main Zooniverse
Dashboard image display tool, which again offers the same stretch settings, as
a starting point for image exploration. Our parameter choices are given in
\Tref{tab:data:humvi}.

@@

Each classification made is logged in a database, storing subject IDs,
volunteer IDs, a timestamp and the classification results (the image
pixel-coordinate positions of every marker placed).  The ``category'' of subject --
whether it is a ``training'' subject (a simulated lens or a known non-lens) or a
``test'' subject (an unseen image drawn from the survey) -- is also recorded.
For training subjects, we also store the ``kind'' of the subject as
a lens (``sim''), or a non-lens (``dud''), and also the ``flavour'' of lens
object if one is present in the image (``lensed galaxy'', ``lensed quasar'' or
``cluster lens'').  This classification is used to provide instant feedback, but
is also the basic measurement used in a probabilistic classification of every
subject based on all image views to date. Not all
volunteers register with the Zooniverse (although all are prompted to do so);
in these cases we record their IP addresses as substitute IDs.
